What is Disputed on the Web?

### 2010-02-25 papers/wicow_claimfinder/claimfinder_final.tex
Spelling fixes

\title{What is disputed on the web?}

@@

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf god} & {\it no significant clusters} & \\
   \hline
   {\bf government} & health care & 2605 \\
                    & united states & 1710 \\
   \hline
   {\bf iraq} & weapons mass destruction & 3874 \\
              & united states & 2972 \\
	      & posed imminent threat & 2547 \\
	      & saddam hussean & 2088 \\
	      & damaging manner justify armed forces & 1814 \\
	      & national security interests & 1673 \\
	      & use nation & 1503 \\
	      & al qaeda & 1200 \\
   \hline
   {\bf israel} & united states & 1211 \\
		& middle east & 556 \\
		& off map & 543 \\
                & west bank & 426 \\
		& second coming & 296 \\
   \hline
   {\bf jesus}  & {\it no significant clusters} & \\
   \hline
   {\bf money}  & root evil & 503 \\
   \hline
    {\bf obama} & working best interests & 1077\\
                & health care & 1074\\
	        & united states & 741 \\
		& birth certificate & 434 \\
		& nobel prize & 311 \\
   \hline
   {\bf president} & united states & 1695 \\
		   & white house & 716 \\
		   & george w & 618 \\
		   & health care & 491 \\
		   & saddam hussein & 369 \\
		   & off map & 363 \\
		   & mahmoud ahmadinejad & 320 \\
		   & sarah palin & 277 \\
   \hline
      {\bf war} & united states & 1323 \\
		& mass destruction & 484 \\
		& middle east & 421 \\
   \hline

>>>>

\title{What is Disputed on the Web?}

@@

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf god} & {\it no significant clusters} & \\
   \hline
   {\bf government} & health care & 2605 \\
                    & united states & 1710 \\
   \hline
   {\bf iraq} & weapons mass destruction & 3874 \\
              & united states & 2972 \\
	      & posed imminent threat & 2547 \\
	      & saddam hussein & 2088 \\
	      & damaging manner justify armed forces & 1814 \\
	      & national security interests & 1673 \\
	      & use nation & 1503 \\
	      & al qaeda & 1200 \\
   \hline
   {\bf israel} & united states & 1211 \\
		& middle east & 556 \\
		& off map & 543 \\
                & west bank & 426 \\
		& second coming & 296 \\
   \hline
   {\bf jesus}  & {\it no significant clusters} & \\
   \hline
   {\bf money}  & root evil & 503 \\
   \hline
    {\bf obama} & working best interests & 1077\\
                & health care & 1074\\
	        & united states & 741 \\
		& birth certificate & 434 \\
		& nobel prize & 311 \\
   \hline
   {\bf president} & united states & 1695 \\
		   & white house & 716 \\
		   & george w & 618 \\
		   & health care & 491 \\
		   & saddam hussein & 369 \\
		   & off map & 363 \\
		   & mahmoud ahmadinejad & 320 \\
		   & sarah palin & 277 \\
   \hline
      {\bf war} & united states & 1323 \\
		& mass destruction & 484 \\
		& middle east & 421 \\
   \hline
